 

### 2019-01-28 Manuscript/Plots/dataplot.tex
Update manuscript

% Created by tikzDevice version 0.11 on 2018-07-02 13:49:21
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.78,184.51) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.74,137.28) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.66,196.39) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (395.12,137.73) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (296.16,142.64) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (300.32,152.77) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (252.19,147.01) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (275.65,144.99) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.42,169.19) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (295.48,141.73) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.48,102.73) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.38,141.15) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.22,165.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.28,141.82) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.93,142.83) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.14,140.40) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.46,141.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (252.70,137.38) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (213.02,142.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (213.66,159.30) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.11,146.53) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.37,148.62) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (332.75,141.10) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.43,147.05) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.15,118.50) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.02,141.70) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.52,151.58) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.92,158.12) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.84,144.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (248.87,141.70) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (115.27,153.34) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.76,150.56) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.88,142.14) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (303.84,140.49) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (255.54,152.49) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (238.26,140.05) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.52, 81.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.08,152.67) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (124.33,154.75) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (284.57,143.29) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (330.47,142.73) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.27,134.29) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (216.19,168.30) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (296.80,143.75) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (290.48,144.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (114.81, 67.58) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.72,146.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.32,126.33) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (281.75,145.53) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (279.13,144.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (260.64,140.58) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.61,143.46) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.81,142.68) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (245.69,150.83) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.60,144.82) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.73, 91.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.57,145.06) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.02,152.93) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (310.91,140.50) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (278.97,136.97) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (246.97,143.78) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.23,133.68) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (246.56,146.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (284.41,132.80) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.22,152.07) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.25,142.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.31,169.02) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.34,140.18) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (295.72,137.19) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 65.96,130.36) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.40, 97.42) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.24,163.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (284.79,189.67) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.06,142.56) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (105.51, 77.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.26,181.23) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (247.12,147.47) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (268.20,136.51) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.21,139.37) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (259.13,145.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (316.60,138.81) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.48,152.66) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (356.86,142.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (321.37,144.48) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.01,141.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (257.61,147.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (297.18,134.55) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.04,137.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.44, 78.13) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (253.82,140.18) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.81,144.62) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.90,149.59) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.74,147.67) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.65,149.14) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (284.88,120.54) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (270.38,138.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.32,142.69) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.63,153.78) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (346.51,135.76) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (126.31,129.29) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.59,138.14) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.83,109.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.55,155.42) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (248.83,143.47) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.63,156.34) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 93.48,136.09) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.44,147.25) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.65,180.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.56,156.05) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (259.32,146.74) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (111.44,151.99) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (219.48,130.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.20,164.64) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.19,157.43) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (335.89,140.67) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.89,159.57) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.22,139.35) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.95,144.27) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.21,153.02) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.28,151.62) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (269.36,130.05) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.85,136.21) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.12,143.35) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.83,133.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.86,145.10) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.61,143.21) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.15,141.54) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (327.05,138.82) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.50,143.52) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.10,141.05) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (291.67,137.53) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (360.51,138.43) circle (  2.25);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,252.94);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.75, 61.20) -- (395.39, 61.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.75, 61.20) -- ( 70.75, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.13, 61.20) -- (117.13, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.51, 61.20) -- (163.51, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.88, 61.20) -- (209.88, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (256.26, 61.20) -- (256.26, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.64, 61.20) -- (302.64, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (349.01, 61.20) -- (349.01, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (395.39, 61.20) -- (395.39, 55.20);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 70.75, 39.60) {0.1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (117.13, 39.60) {0.2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (163.51, 39.60) {0.3};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (209.88, 39.60) {0.4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (256.26, 39.60) {0.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (302.64, 39.60) {0.6};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (349.01, 39.60) {0.7};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (395.39, 39.60) {0.8};

@@

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 10.80,132.47) {IPC location};
\end{scope}
\end{tikzpicture}

>>>>

% Created by tikzDevice version 0.11 on 2019-01-11 18:28:29
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.44,124.69) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (126.12,176.35) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (395.12,196.40) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.43,184.51) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.57,196.39) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.60,102.73) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (268.97,142.83) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (144.34,118.50) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.61, 81.92) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (386.17,144.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.76, 67.58) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.69,142.68) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.30, 91.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 67.40,130.36) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.59,181.23) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.57,139.37) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (291.52,144.62) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (378.23,120.54) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (357.63,138.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.10,129.29) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.60,109.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (356.19,130.05) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.97,136.21) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (245.65,143.52) circle (  2.25);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,252.94);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 74.22, 61.20) -- (403.43, 61.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 74.22, 61.20) -- ( 74.22, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.06, 61.20) -- (140.06, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (205.90, 61.20) -- (205.90, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.75, 61.20) -- (271.75, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (337.59, 61.20) -- (337.59, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (403.43, 61.20) -- (403.43, 55.20);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 74.22, 39.60) {0.1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (140.06, 39.60) {0.2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (205.90, 39.60) {0.3};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (271.75, 39.60) {0.4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (337.59, 39.60) {0.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (403.43, 39.60) {0.6};

@@

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 10.80,132.47) {IPC};
\end{scope}
\begin{scope}
\path[clip] ( 49.20, 61.20) rectangle (408.42,203.75);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (307.75,165.69) --
	(310.78,160.44) --
	(304.72,160.44) --
	(307.75,165.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (279.23,156.95) --
	(282.26,151.70) --
	(276.20,151.70) --
	(279.23,156.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (311.37,146.41) --
	(314.40,141.16) --
	(308.34,141.16) --
	(311.37,146.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (430.67,147.56) --
	(433.62,142.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.62,142.31) --
	(427.64,142.31) --
	(430.67,147.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.81,136.83) --
	(233.84,131.58) --
	(227.78,131.58) --
	(230.81,136.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.06,136.63) --
	(220.09,131.39) --
	(214.03,131.39) --
	(217.06,136.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (363.44,149.83) --
	(366.47,144.58) --
	(360.41,144.58) --
	(363.44,149.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (341.18,153.72) --
	(344.21,148.47) --
	(338.15,148.47) --
	(341.18,153.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (290.02,150.26) --
	(293.05,145.01) --
	(286.99,145.01) --
	(290.02,150.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.60,143.72) --
	(390.63,138.47) --
	(384.57,138.47) --
	(387.60,143.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.74,147.88) --
	(421.77,142.63) --
	(415.71,142.63) --
	(418.74,147.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (403.53,148.36) --
	(406.56,143.11) --
	(400.50,143.11) --
	(403.53,148.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.84,140.78) --
	(180.87,135.53) --
	(174.81,135.53) --
	(177.84,140.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (394.24,146.14) --
	(397.27,140.89) --
	(391.21,140.89) --
	(394.24,146.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (400.15,156.27) --
	(403.18,151.02) --
	(397.12,151.02) --
	(400.15,156.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (331.82,150.51) --
	(334.85,145.26) --
	(328.79,145.26) --
	(331.82,150.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (365.13,148.48) --
	(368.16,143.24) --
	(362.10,143.24) --
	(365.13,148.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (288.12,172.69) --
	(291.15,167.44) --
	(285.09,167.44) --
	(288.12,172.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (393.28,145.23) --
	(396.31,139.98) --
	(390.25,139.98) --
	(393.28,145.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.18,144.65) --
	(227.21,139.40) --
	(221.15,139.40) --
	(224.18,144.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.43,169.45) --
	(218.46,164.20) --
	(212.40,164.20) --
	(215.43,169.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (297.87,145.31) --
	(300.90,140.07) --
	(294.84,140.07) --
	(297.87,145.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (332.53,140.88) --
	(335.56,135.63) --
	(329.50,135.63) --
	(332.53,140.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (276.19,146.44) --
	(279.22,141.20) --
	(273.16,141.20) --
	(276.19,146.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (277.12,162.80) --
	(280.15,157.56) --
	(274.09,157.56) --
	(277.12,162.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.83,150.02) --
	(199.86,144.78) --
	(193.80,144.78) --
	(196.83,150.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (344.84,152.12) --
	(347.87,146.87) --
	(341.81,146.87) --
	(344.84,152.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.46,150.55) --
	(285.49,145.30) --
	(279.43,145.30) --
	(282.46,150.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.91,145.20) --
	(301.94,139.96) --
	(295.88,139.96) --
	(298.91,145.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (279.76,155.08) --
	(282.79,149.83) --
	(276.73,149.83) --
	(279.76,155.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.67,161.61) --
	(179.70,156.37) --
	(173.64,156.37) --
	(176.67,161.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (327.10,145.20) --
	(330.13,139.95) --
	(324.07,139.95) --
	(327.10,145.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.43,156.84) --
	(140.46,151.59) --
	(134.39,151.59) --
	(137.43,156.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.48,154.06) --
	(267.51,148.81) --
	(261.45,148.81) --
	(264.48,154.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.90,145.64) --
	(227.93,140.39) --
	(221.87,140.39) --
	(224.90,145.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (405.14,143.98) --
	(408.17,138.74) --
	(402.11,138.74) --
	(405.14,143.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (336.56,155.98) --
	(339.59,150.74) --
	(333.53,150.74) --
	(336.56,155.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.03,143.55) --
	(315.06,138.30) --
	(309.00,138.30) --
	(312.03,143.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.78,146.79) --
	(380.81,141.54) --
	(374.75,141.54) --
	(377.78,146.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (216.93,137.79) --
	(219.96,132.54) --
	(213.90,132.54) --
	(216.93,137.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (280.70,171.80) --
	(283.73,166.55) --
	(277.67,166.55) --
	(280.70,171.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (395.15,147.25) --
	(398.18,142.00) --
	(392.12,142.00) --
	(395.15,147.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (111.08,149.95) --
	(114.11,144.70) --
	(108.05,144.70) --
	(111.08,149.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.58,129.83) --
	(103.61,124.58) --
	( 97.55,124.58) --
	(100.58,129.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (373.78,149.03) --
	(376.81,143.79) --
	(370.75,143.79) --
	(373.78,149.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (370.05,148.44) --
	(373.08,143.19) --
	(367.02,143.19) --
	(370.05,148.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (375.00,146.96) --
	(378.03,141.71) --
	(371.97,141.71) --
	(375.00,146.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (322.59,154.33) --
	(325.62,149.08) --
	(319.56,149.08) --
	(322.59,154.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.84,148.32) --
	(424.87,143.07) --
	(418.81,143.07) --
	(421.84,148.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.19,148.56) --
	(223.22,143.31) --
	(217.16,143.31) --
	(220.19,148.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.92,156.43) --
	(301.95,151.18) --
	(295.89,151.18) --
	(298.92,156.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (415.18,144.00) --
	(418.21,138.75) --
	(412.15,138.75) --
	(415.18,144.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (369.84,140.47) --
	(372.87,135.22) --
	(366.81,135.22) --
	(369.84,140.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (324.40,147.27) --
	(327.43,142.03) --
	(321.37,142.03) --
	(324.40,147.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (250.94,137.18) --
	(253.97,131.93) --
	(247.91,131.93) --
	(250.94,137.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.83,150.45) --
	(326.86,145.20) --
	(320.80,145.20) --
	(323.83,150.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.32,155.57) --
	(238.35,150.32) --
	(232.29,150.32) --
	(235.32,155.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (296.40,145.95) --
	(299.43,140.70) --
	(293.37,140.70) --
	(296.40,145.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (292.22,172.52) --
	(295.25,167.27) --
	(289.19,167.27) --
	(292.22,172.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (330.60,143.68) --
	(333.63,138.43) --
	(327.57,138.43) --
	(330.60,143.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (393.62,140.69) --
	(396.65,135.44) --
	(390.59,135.44) --
	(393.62,140.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.33,100.91) --
	(207.36, 95.67) --
	(201.30, 95.67) --
	(204.33,100.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.65,166.95) --
	(188.68,161.70) --
	(182.62,161.70) --
	(185.65,166.95);
